Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-10-05 paper/virtual_cytoplasm_v2.tex
Updated

\subsubsection{Structural dynamics}
{\bf THIS PARAGRAPH REPEATS AND CONTRADICTS ITSELF. IS FLEXIBILITY
  AFFECTED OR NOT? FROM THE GRAPH I WOULD SAY THE THE FIVE PROTEINS
  NOTED BELOW ARE MUCH MORE FLEXIBLE, NOT SLIGHTLY. ONE WAY OF
  QUANTIFYING THIS IS TO COMPUTE THE AVERAGE OF THE MEAN SQUARE
  FLUCTUATION OVER THE WHOLE PROTEIN, THAT IS BEFORE TAKING SQUARE
  ROOTS OF COURSE AND PLOTTING THAT IN A BAR GRAPH. THEN THIS FIGURE
  CAN GO TO SUPPORTING.}  Proteins are slightly more flexible in the
crowded than in the dilute environment. Root mean square fluctuation
(RMSF) calculations show that the flexibility profile of the proteins
is not affected by crowding, which is in agreement with our results
showing that the structural integrity of the proteins is not changed
significantly in the cytoplasm model (Fig.~\ref{fig:rmsf}).  On the
other hand, there are some small differences between the dilute and
crowding conditions. In most cases (TufA, MetE, AhpC, CspC and Ppa),
proteins are slightly more flexible in the cytoplasm model
(Fig.~\ref{fig:rmsf}). This is in agreement with data showing that
nonspecific interactions with crowders can lead to destabilization of
proteins~\cite{Feig2011, miklos2011, Wang2012b}.

>>>>

\subsubsection{Structural dynamics}
{\bf THIS PARAGRAPH REPEATS AND CONTRADICTS ITSELF. IS FLEXIBILITY
  AFFECTED OR NOT? FROM THE GRAPH I WOULD SAY THE THE FIVE PROTEINS
  NOTED BELOW ARE MUCH MORE FLEXIBLE, NOT SLIGHTLY. ONE WAY OF
  QUANTIFYING THIS IS TO COMPUTE THE AVERAGE OF THE MEAN SQUARE
  FLUCTUATION OVER THE WHOLE PROTEIN, THAT IS BEFORE TAKING SQUARE
  ROOTS OF COURSE AND PLOTTING THAT IN A BAR GRAPH.}  Proteins are slightly more flexible in the
crowded than in the dilute environment. Root mean square fluctuation
(RMSF) calculations show that the flexibility profile of the proteins
is not affected by crowding, which is in agreement with our results
showing that the structural integrity of the proteins is not changed
significantly in the cytoplasm model (Fig.~\ref{fig:rmsf}).  On the
other hand, there are some small differences between the dilute and
crowding conditions. In most cases (TufA, MetE, AhpC, CspC and Ppa),
proteins are slightly more flexible in the cytoplasm model
(Fig.~\ref{fig:rmsf}). This is in agreement with data showing that
nonspecific interactions with crowders can lead to destabilization of
proteins~\cite{Feig2011, miklos2011, Wang2012b}.
